\documentclass{article}
%\usepackage{neurips_2024}
\usepackage[preprint]{neurips_2024}
%\usepackage[final]{neurips_2024}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colorsCSCI

% change this to your project's title
\title{CSCI 566 - Final Project Report}

\author{%
  Team Member \#1 \\
  \texttt{team-member1@usc.edu} \\
  $\dots$ \\
  \textit{(please include all team member names and emails here)}
  \\ \\
  \textcolor{red}{\textbf{Due}: \textit{11:59PM PT, Dec. 12 on Brightspace}}
}

\begin{document}

\maketitle

\begin{abstract}
\textit{(Add your project abstract here: this should concisely capture the general aims of your project, the key elements of your approach, and the theoretical result or application you're targeting)}
\end{abstract}

(your final report here) 

\section*{References}
\textit{(Add your references here, or include them from a separate bibtex file as needed.)}
\\

{
\small
[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms for
connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and T.K.\ Leen
(eds.), {\it Advances in Neural Information Processing Systems 7},
pp.\ 609--616. Cambridge, MA: MIT Press.

[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS: Exploring
  Realistic Neural Models with the GEneral NEural SImulation System.}  New York:
TELOS/Springer--Verlag.

[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of learning and
recall at excitatory recurrent synapses and cholinergic modulation in rat
hippocampal region CA3. {\it Journal of Neuroscience} {\bf 15}(7):5249-5262.
}

\end{document}